Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?

### 2018-09-12 outputs/docs/events/paper.Rmd
Get example STM model working

---
title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
author:
  - Monica Alexander^[University of Toronto, Statistical Sciences and Sociology Departments, \texttt{monica.alexander@utoronto.ca}.]
  - Rohan Alexander^[Australian National University, Research School of Economics, \texttt{rohan.alexander@anu.edu.au}.]
date: "`r format(Sys.time(), '%d %B %Y')`"
fontsize: 12pt
output: 
  pdf_document:
    number_sections: true
bibliography: ../bibliography.bib
abstract: |
  We use a structural text model to explore the impact of various events on what was said in Australian state and Commonwealth parliaments from the year they were established (mid-1800s for most of the states, and 1901 for the Commonwealth) through to 2017. We find that 1) [TBD]; 2) [TBD]; and 3) [TBD].

@@

# Introduction
New governments often go out of their way to be different to the governments they replace. For instance, consider Kevin Rudd's apology to Indigenous Australians which supported by all living Prime Ministers apart from his immediate predecessor. Similarly, significant events can alter the course of a government. For instance, consider the change in the Howard government after the 9/11 attacks. However it is not so clear which events drive changes in topics, for instance, do they change when the government is replaced by another of its own party? And which events are temporary, for instance when an economic crisis abates, do the topics return to pre-crisis levels?

>>>>

---
title: "Nobody expects the Spanish Inquisition: Which events drive topic change in Australian parliaments?"
author:
  - Monica Alexander^[University of Toronto, Statistical Sciences and Sociology Departments, \texttt{monica.alexander@utoronto.ca}.]
  - Rohan Alexander^[Australian National University, Research School of Economics, \texttt{rohan.alexander@anu.edu.au}.]
date: "`r format(Sys.time(), '%d %B %Y')`"
fontsize: 12pt
output: 
  pdf_document:
    number_sections: true
bibliography: ../bibliography.bib
abstract: |
  We use a structural text model to explore the impact of various events on what was said in Australian state and Commonwealth parliaments from the mid-1800s through to 2017. We find that 1) changes of government where the party in power also changes, result in significant changes in topics discussed in parliament, but when the party does not change the topics are unchanged; 2) polling results do not have a significant effect; 3) economic changes, such as financial crises have a significant effect; and 4) other events, such as an unexpected attack tend not to have a prolonged change.

@@

# Introduction
New governments often go out of their way to be different to the governments they replace. For instance, Kevin Rudd's apology to Indigenous Australians was supported by all living former Prime Ministers apart from his immediate predecessor. Similarly,  Similarly, significant events can alter the course of a government. For instance, consider the change in the Howard government after the 9/11 attacks. However it is not so clear which events drive changes in topics, for instance, do they change when the government is replaced by another of its own party? And which events are temporary, for instance when an economic crisis abates, do the topics return to pre-crisis levels?
